Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
completed

# Creating new entries for multiple people in one disposition
stop_df <- stop_df %>%
  separate(Dispositions, into = c("1", "2", "3", "4", "5"), extra = "merge", fill = "right") %>%
  gather(key = Individual, value = Dispositions, -Incident.Type, -Incident.Number, -Call.Date.Time, -Location, -Other) %>%
  na.omit() %>%
  arrange(Incident.Number)

@@

```

>>>>

# Creating new entries for multiple people in one disposition
stop_df <- stop_df %>%
  separate(Dispositions, into = c("1", "2", "3", "4", "5"), extra = "merge", fill = "right") %>%
  gather(key = Individual, value = Dispositions, -Incident.Number, -Incident.Type, -Call.Date.Time, -Other, -Location) %>%
  na.omit() %>%
  arrange(Incident.Number)

@@
